---
title: "Our World in Data: Key Crop Yields"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Our World in Data: Key Crop Yields}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 6.5,
  fig.height = 5
)
```

```{r setup}
library(cwdata)
```

  - A dataset containing crop yields for countries over time. Yields are measured in tonnes per hectare for `r length(unique(key_crop_yields$crop))` crops which are `r glue::glue_collapse(unique(key_crop_yields$crop), sep = ", ", last = "and")`.

  - The dataset has been sourced from [Our World in Data](https://ourworldindata.org/crop-yields)  and [Tidy Tuesday](https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-09-01/readme.md)
"key_crop_yields" and it can be called with _key_crop_yields_ by loading the _cwdata_ package

It can be accessed by

```{r}
library(cwdata)
library(tibble)
key_crop_yields
```

# Exploration fo the data
  
```{r examples}
library(ggplot2)
library(dplyr)
key_crop_yields %>%
  filter(entity == "Australia") %>%
  ggplot(aes(x = year,
             y = tonnes_per_hectare)) + 
  geom_line() +
  facet_wrap(~crop, scales = "free_y") +
  labs(y = "tonnes per hectar",
       x = "year")


key_crop_yields %>%
  ggplot(aes( x = tonnes_per_hectare,
         y = crop)) +
  geom_point()


key_crop_yields %>%
  filter(crop == "wheat") %>%
  group_by(entity, year) %>%
  summarise(n = sum(tonnes_per_hectare)) %>%
  head(n = 500) %>%
  ggplot(aes(x = year,
             y = n,
             color = entity)) +
  geom_line() +
  labs(x = "Wheat yield, tonnes per hectar")
```
